Journey: A Study of Scalabilty of Memory Management in Linux

### 2017-04-28 paper.tex
Fixed a couple of minor typos
Added a citation

@@

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for \texttt{rand} benchmark.}
    \label{swap_rss}
\end{figure}

@@

Prefetching pages from swap space can offer a way to mitigate the overhead of
memory overcommitment, possibly making large virtual machines a viable
mechanism for studying large memory systems. When there is significant memory
pressure, even pages which are likely to be accessed soon are swapped out to
disk. They are faulted back into memory when accessed, resulting in significant
performance cost.  Charm++ uses a programming model where computations can be
scheduled by the language runtime. A designated thread can prefetch pages
required by a computation, averting page faults \cite{charmpp}. Rather than
implement page prefetching in a language runtime, one might implement a
prefetcher in the swapping subsystem, making it general purpose. A large body
of work already exists on hardware prefetching for processor caches, on which a
swap prefetcher might draw for inspiration (TODO: cite). However, this approach
can only work if page access patterns are predictable. Moreover, the high
latency of disks implies that prefetchers would have to predict the very
distant future (e.g. seconds ahead of execution). (TODO: Mike's comment on the
previous version of this paragraph said that it was ``too distant/off topic''.
Is it better now? I feel like prefetching was an idea that we considered too
much to leave out...)

>>>>

\begin{figure}[t]
    \includegraphics[width=\columnwidth]{figures/swap_rss}
    \caption{RSS while touching pages while swapping for \texttt{rand} benchmark.
    \label{fig:swap_rss}}
\end{figure}

@@

@@

Prefetching pages from swap space can offer a way to mitigate the overhead of
memory overcommitment, possibly making large virtual machines a viable
mechanism for studying large memory systems. When there is significant memory
pressure, even pages which are likely to be accessed soon are swapped out to
disk. They are faulted back into memory when accessed, resulting in significant
performance cost.  Charm++ uses a programming model where computations can be
scheduled by the language runtime. A designated thread can prefetch pages
required by a computation, averting page faults \cite{charmpp}. Rather than
implement page prefetching in a language runtime, one might implement a
prefetcher in the swapping subsystem, making it general purpose. A large body
of work already exists on hardware prefetching for processor caches, on which a
swap prefetcher might draw for inspiration \cite{prefetching}. However, this approach
can only work if page access patterns are predictable. Moreover, the high
latency of disks implies that prefetchers would have to predict the very
distant future (e.g. seconds ahead of execution). (TODO: Mike's comment on the
previous version of this paragraph said that it was ``too distant/off topic''.
Is it better now? I feel like prefetching was an idea that we considered too
much to leave out...)
